Untitled

### 2017-06-27 LowUseLondon.Rmd
UPdateed leaflet plotter
Creates a leaflet plot automatically subsetting the spatial dataframe. this is helpful as it allows multiple LADs to be plotted at once, e.g the whole of Cumbria.

sum(Chelseainfo$LowUse)/sum(Chelseainfo$Homes)

#T test if there is a significant difference between 
v <- Chelseainfo %>% filter(LAD11CD =="E09000020")

#low-use value chelsea
sum(v$MeanPrice*v$LowUse)
ChelMeanPrice <- (sum(v$MeanPrice*v$counts)/sum(v$counts))
ChelLowMean<- sum(v$MeanPrice*v$LowUse)/sum(v$LowUse)
ChelLowMean/ChelMeanPrice
v<- rep(v$MeanPrice, times = v$LowUse)-ChelMeanPrice

@@

 1762724.8-  426694.1

   test <- chelstrap %>% 
    select(class,ID, Homes, LowUse, HomesValue, LowUseValue) %>%
    group_by(ID, class) %>%
    summarise_all(funs(sum)) %>%
    mutate(HomesPrice = HomesValue/Homes,
           LowUsePrice = LowUseValue/LowUse)

ggplot(test, aes(x= class, y = LowUsePrice, fill = class)) + geom_boxplot()
 ggplot(test, aes(x= class, y = HomesPrice, fill = class)) + geom_boxplot()

  ggplot(test, aes(x= log(LowUsePrice), y = log(HomesPrice), colour = class)) + geom_point()  
```

>>>>

#percent of chelsea low-use
sum(Chelseainfo$LowUse)/sum(Chelseainfo$Homes)

#low-use value chelsea
sum(v$MeanPrice*v$LowUse)
ChelMeanPrice <- (sum(v$MeanPrice*v$counts)/sum(v$counts))

@@

 #boxplot comparison
Chelttest$data.frame %>%
  select(HomesPrice, LowUsePrice) %>%
  gather(key ="type", value = "MeanPrice") %>%
ggplot(., aes(x= type, y = MeanPrice, fill = type)) + geom_boxplot()

#density plot comparison
Chelttest$data.frame %>%
  select(HomesPrice, LowUsePrice) %>%
  gather(key ="type", value = "MeanPrice") %>%
ggplot(., aes(x = MeanPrice, fill = type)) + geom_density()

### 2017-06-27 PlotwithLeaflet.Rmd
Fixing some bugs
there were all kinds of wied going on ... I think this has fixed it.
UPdateed leaflet plotter
Creates a leaflet plot automatically subsetting the spatial dataframe. this is helpful as it allows multiple LADs to be plotted at once, e.g the whole of Cumbria.

```{r}
setwd(gitpage)
z <- MakeLeaflet("chelsea", Chelseainfo)
z
saveWidget(z, file="ChelseaLowUse.html", selfcontained = TRUE )

z<- MakeLeaflet("lambeth", Lambethinfo, c(0:5))
saveWidget(z, file="LambethLowUSe.html", selfcontained = TRUE )

@@

>>>>

```{r}
setwd(gitpage)
z <- MakeLeaflet(Chelseainfo)
z
saveWidget(z, file="ChelseaLowUse.html", selfcontained = TRUE )

z<- MakeLeaflet(Lambethinfo, c(0:5))
saveWidget(z, file="LambethLowUSe.html", selfcontained = TRUE )

@@

```{r}
z <- MakeLeaflet(Camdeninfo)
z
saveWidget(z, file="CamdenLowUse.html", selfcontained = TRUE )
```
